\documentclass{jsarticle}
\usepackage{amsmath,amssymb,amsfonts}

\begin{document}
二次方程式の解の公式は
\begin{equation}
x = \frac{-b\pm\sqrt{b^2-4ac}}{2a}
\end{equation}
\end{document}




アナコンダプロンプトでコード動かすときはベース環境でやるな！！！！！！！！


python main.py confs/GTCNN experiment.color=1 experiment.test_only=True dataset.test_set=[Set12,BSD68,Urban100] dataset.test_root=E:\Study\GTCNN_train\Datasets\test\ experiment.best_model=SAGTCNN_g_50_D1_down4

python main.py confs/GTCNN experiment.color=1 experiment.test_only=True experiment.best_model=Gray50_GTCNN_D1 dataset.test_set=[Set12,BSD68,Urban100] dataset.test_root=E:\Study\GTCNN_train\Datasets\test\

ドライブ移動
cd /d E:

改造したGTCNNのPath
cd E:\Study\22.B.Udou\21.M.Imai-main\DN

純正GTCNNのPath
cd E:\Study\real.21.M.Imai-main\DN

python main.py confs/GTCNN experiment.color=1 experiment.random_corp=True experiment.large_size=512 experiment.stride=512 dataset.test_set=[Set12,BSD68,Urban100] dataset.train_set=[DIV2K] dataset.val_set=[BSD400] dataset.test_root=E:\Study\GTCNN_train\Datasets\test\ dataset.train_root=E:\Study\GTCNN_train\Datasets\train\ dataset.val_root=E:\Study\GTCNN_train\Datasets\val\ experiment.epoch_num=600

experiment.sigma=50 experiment.comet_disabled=False experiment.saveImage=True experiment.save_checkpoint=True 



experiment.test_only=True
experiment.comet_disabled=False
experiment.saveImage=True
experiment.best_model=SAGTCNN_g_50_D1_midSA

#### RealNoise ##########
cd E:\Study\22.B.Udou\21.M.Imai-main\RN

python main.py confs/GTCNN experiment.color=3 experiment.random_corp=True experiment.large_size=512 experiment.stride=512 dataset.test_set=[SSID_patched] dataset.train_set=[SSID] dataset.val_set=[SSID] dataset.test_root=D:\Study\GTCNN_train\Datasets\test\ dataset.train_root=D:\Study\GTCNN_train\Datasets\train\ dataset.val_root=D:\Study\GTCNN_train\Datasets\val\ experiment.epoch_num=600


・Datasets
test
 -Set12,BSD68,Urban100
train
 -DIV2K
made train
 -DIV2KandSIDD
・model
SAGTCNN_g_50_D1_midSA
SAGTCNN_g_50_D1_down4